---
title: "Curriculum Vitae"
toc: true
toc-depth: 2
toc-location: right
---

```{r}
#| include: false
source(file.path(Sys.getenv("QUARTO_PROJECT_DIR", ".."), "R", "site.R"))

# Non-empty text values only. Fields can arrive missing (NULL), as NA, as an
# empty string, or as a one-item string where a list was expected; all of these
# are flattened to a plain character vector with NA and blanks dropped.
clean <- function(x) {
  x <- unlist(x, use.names = FALSE)
  if (is.null(x)) return(character())
  x <- trimws(as.character(x[!is.na(x)]))
  x[nzchar(x)]
}

# Join the non-empty parts, so a missing part never leaves "NA" or a stray comma.
join <- function(..., sep = ", ") paste(clean(c(...)), collapse = sep)

# End text with a period unless it already ends in terminal punctuation.
sentence <- function(x) {
  x <- paste(clean(x), collapse = " ")
  if (!nzchar(x) || grepl("[.?!]$", x)) x else paste0(x, ".")
}

entry <- function(what, when = NULL, with = NULL, why = NULL) {
  when <- clean(when)
  with <- clean(with)
  why <- clean(why)
  cat("**", md(what), "**", if (length(when)) paste0(" <span class='cv-when'>", md(when[1]), "</span>"), "  \n", sep = "")
  if (length(with)) cat(with[1], "\n", sep = "")
  if (length(why)) cat("\n", paste0("- ", md(why), collapse = "\n"), "\n", sep = "")
  cat("\n")
}

# One bulleted list item per row, skipping rows whose text comes out empty.
bullets <- function(x) {
  x <- clean(x)
  if (length(x)) cat(paste0("- ", x, collapse = "\n"), "\n", sep = "")
}
```

[<i class="bi bi-file-earmark-pdf" aria-hidden="true"></i> Download PDF](../files/Miramonti_CV.pdf){.btn .btn-primary}

Publications and presentations have their own pages: [Publications](../publications.qmd) · [Talks & presentations](../talks.qmd).

## Education

```{r}
#| results: asis
d <- cv_data("education")
for (i in seq_len(nrow(d))) entry(d$degree[i], d$dates[i], md(join(d$institution[i], d$location[i])), if ("details" %in% names(d)) d$details[[i]])
```

## Academic professional experience

```{r}
#| results: asis
d <- cv_data("positions")
for (i in seq_len(nrow(d))) entry(d$title[i], d$dates[i], md(join(d$unit[i], d$institution[i])), if ("description" %in% names(d)) d$description[[i]])
```

## Software

```{r}
#| results: asis
d <- cv_data("software_dev")
for (i in seq_len(nrow(d))) entry(d$name[i], d$when[i], md(join(d$role[i])), if ("description" %in% names(d)) d$description[[i]])
```

## Manuscripts in progress

```{r}
#| results: asis
d <- cv_data("manuscripts")
ord <- order(match(d$status, c("Under review", "Revise & Resubmit", "Accepted", "In progress")))
bullets(vapply(ord, function(i) {
  status <- clean(d$status[i])
  paste0(join(md(sentence(d$authors[i])), md(sentence(d$title[i])), sep = " "),
         if (length(status)) paste0(" *", md(status[1]), "*"))
}, character(1)))
```

## Technical & evaluation reports

```{r}
#| results: asis
d <- cv_data("reports")
bullets(vapply(seq_len(nrow(d)), function(i) {
  date <- clean(d$date[i])
  head <- join(d$authors[i], if (length(date)) paste0("(", date[1], ")"), sep = " ")
  join(md(sentence(head)), md(sentence(d$title[i])), md(sentence(d$outlet[i])), sep = " ")
}, character(1)))
```

## Invited & guest lectures

```{r}
#| results: asis
d <- cv_data("lectures")
for (i in seq_len(nrow(d))) entry(d$title[i], d$date[i], md(join(d$context[i])))
```

## Mentoring

```{r}
#| results: asis
d <- cv_data("mentoring")
for (i in seq_len(nrow(d))) entry(d$role[i], d$dates[i], md(join(d$program[i], d$institution[i])))
```

## Additional professional training

```{r}
#| results: asis
d <- cv_data("training")
for (i in seq_len(nrow(d))) {
  series <- clean(d$series[i])
  entry(d$title[i], d$date[i], md(join(d$presenter[i], if (length(series)) paste0("(", series[1], ")"), sep = " ")))
}
```

## Awards, fellowships, & scholarships

```{r}
#| results: asis
d <- cv_data("awards")
for (i in seq_len(nrow(d))) entry(d$award[i], d$dates[i], md(join(d$organization[i])))
```

## Professional service

```{r}
#| results: asis
d <- cv_data("service")
for (i in seq_len(nrow(d))) entry(d$role[i], d$dates[i], md(join(d$organization[i])))
```

## Professional associations

```{r}
#| results: asis
d <- cv_data("associations")
for (i in seq_len(nrow(d))) entry(d$organization[i], d$dates[i], md(join(d$membership[i])))
```

## Professional credentials

```{r}
#| results: asis
d <- cv_data("credentials")
for (i in seq_len(nrow(d))) entry(d$credential[i], d$status[i], md(join(d$organization[i])))
```

## Technical skills

```{r}
#| results: asis
d <- cv_data("software")
bullets(vapply(seq_len(nrow(d)), function(i) {
  tools <- clean(d$tools[i])
  if (length(tools)) paste0("**", md(join(d$category[i])), ":** ", md(tools[1])) else ""
}, character(1)))
cat("\n### Laboratory assessments\n\n")
bullets(md(clean(cv_data("lab_skills")$skill)))
```
